SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-06 scipy-1.0/paper.tex
Drafted FORTRAN section of language choices description along with appropriate citations.

>>>>

While it is not surprising that Python is heavily used in SciPy, the
usage distribution of the other languages warrants some discussion. Fortran
is an extremely well-established scientific programming language, both
for historical reasons and because of its continued excellent
performance\cite{Koelbel:1993:HPF:562354}. We
wrap the FFTPACK Fortran library for performing Fourier
transforms\cite{SWARZTRAUBER198445, SWARZTRAUBER198251} since
this library has been a standard in the field for 33 years and has a license
that is compatible with our own. Likewise, we wrap the Fortran source
for ODEPACK\cite{citeulike:2644528} as it has been  trusted for the initial 
value problem for ordinary differential equation systems for 30 years. For
similar reasons we also warp the Fortran libraries QUADPACK\cite{1983qspa.book.....P} (for numerical
integration of one-dimensional functions), FITPACK\cite{Dierckx:1993:CSF:151103} (curve-fitting /
interpolation), ODRPACK\cite{ODRPACK_Boggs} (orthogonal distance regression),
MINPACK\cite{osti_6997568} (minimization of linear and nonlinear equations),
ARPACK\cite{leh:sor:yan96} (solving large scale eigenvalue problems), 
ALGORITHM 644\cite{Amos:1986:APP:7921.214331} (handling Bessel Functions), and 
CDFLIB\cite{CDFLIB_site} (evaluation of cumulative density functions).
